\documentclass{article}
% if you need to pass options to natbib, use, e.g.:
    % \PassOptionsToPackage{numbers, compress}{natbib}
% before loading project
% ready for submission
\usepackage[preprint]{zsupport/project}
% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{project}

\input{zsupport/algo}
\input{zsupport/english}
\input{zsupport/figure}
\input{zsupport/linking}
\input{zsupport/math}
\input{zsupport/mathenv}
\input{zsupport/mathvar}
\input{zsupport/refer}
\input{zsupport/table}
\input{zsupport/misc}

% https://www.overleaf.com/learn/latex/Questions/How_do_I_add_additional_author_names_and_affiliations_to_my_paper%3F
\usepackage{authblk}

\usepackage[yyyymmdd,hhmmss]{datetime}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{listings}
\usepackage{algorithm}     
\usepackage{algorithmic} 

\usepackage{float}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Project Milestone 2: Finding Optimal Taxation Policy With RL}

\author[1]{Ardhito Nurhadyansah}
\author[2]{Ian Suryadi Timothy H}
\affil[1]{2106750206}
\affil[2]{2106750875}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle

\begin{abstract}
    In this project, we simulate the economic output, given a tax policy. This project is adapted from the work of (Zheng et al., 2020) , where the model is comprises of two interconnected Markov Decision Process. The inner-loop MDP is the agents MDP, which have partial observations and interact to each other in a gather-and-build simulation. The outer-loop MDP models a social planner that find the optimal tax policy to maximize a social welfare function, which is formulated by a product of equality and economic productivity.
\end{abstract}
    
\input{problem_formulation}

\input{solution_design}

\input{preliminary_analysis}


\input{modeling}
\input{algorithm}
\input{experiment}

\section{Citations and References}


% \bibliography{main}
% \bibliography{ref/zheng_2020_aieconomist}
% \bibliographystyle{apalike}
Zheng, S., Trott, A., Srinivasa, S., Naik, N., Gruesbeck, M., Parkes, D. C., & Socher, R. (2020). The AI Economist: Improving equality and productivity with AI-driven tax policies. arXiv. https://arxiv.org/abs/2004.13332

Schulman, J., Wolski, F., Dhariwal, P., Radford, A., & Klimov, O. (2017). Proximal Policy Optimization Algorithms. arXiv. https://arxiv.org/abs/1707.06347

\end{document}